Reproducibility in Plant Pathology

### 2021-06-02 README.rmd
Clarify directory structure in the README.md and update affiliation

You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/master.zip>

@@

@@

Adam H Sparks, Associate Professor, Centre for Crop Health  
University of Southern Queensland  
Toowoomba, Queensland 4350

+61 (7) 4631 1948   <adam.sparks@usq.edu.au>

>>>>

You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/main.zip>

@@

The file structure follows a normal R package with one exception.
The top-level "/analysis" directory contains the directories and files necessary to reknit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".

@@

Adam H Sparks
Senior Research Scientist
Farming Systems Innovation
Primary Industries Development
Department of Primary Industries and Regional Development
Level 5, 1 Nash St Perth WA 6000
